Generality in food webs scales with species richness but not with latitude

### 2015-06-22 manuscript/latitudepaper.tex
Added DBS comments except for finding more refs

\title{Generality in food webs scales with species richness but not with latitude}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2\\ Canada\\}

@@

\vspace{-0.2 in}

@@

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships with species richness
in the estuarine, marine, and terrestrial food webs, there were strong effects
of latitude on scaling relationships in the freshwater food webs. In these
communities, the latitude-niche breadth hypothesis appears to hold true while
in other habitat types niche breadth appears to vary little. These contrasting
findings indicate that it may be more important to account for habitat than
latitude when exploring gradients in food-web structure.

@@

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialisation (i.e., the breadth of the Eltonian niche ~\citep{Elton1927}) of species within food webs.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics~\citep{Dyer2007,Marra1997}
  but see~\citep{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialisation by examining the shape of the scaling 
  relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialisation implied by
  the ``latitude-niche breadth hypothesis''.

@@

    As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
    is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
    sets to form ``trophic species'' webs (e.g.~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
    is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
    species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
    of the dataset; in each case using the number of species and 
    links in each web to calculate the mean link density (number of links per species), mean generality 
    (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
    The version of the dataset used did not qualitatively change the results, suggesting that
    the scaling relationships between species richness, other food-web properties, and latitude are very 
    similar whether or not redundant species are included. For simplicity, we present only
    the results for the original webs.

@@

    The scaling relationships between link density ($Z$) and species richness ($S$)
    has been shown to be a power law~\citep{Riede2010} of the form

@@

    \noindent As the two forms imply different error distributions, neither of which has strong
    \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
    to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
    The logarithmic form (equation~\ref{Loglog}) provided the better fit to the data,
    as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
    We therefor used logarithmic models throughout the rest of the study.

@@

    After determining the appropriate form of the scaling relationship, we
    then assessed the impact of latitude on the scaling relationships between
    species richness and  link density, generality, vulnerability. In the
    context of the scaling relationships above, note  that this implies that
    we aim to determine the effect of latitude on the scaling exponent
    $\beta$. As when examining the relationships between latitude and each
    food  web property directly, we included a categorical variable for
    ecosystem type (stream, lake,  terrestrial, marine, or estuary), as well
    as interactions between food web type and latitude.

@@

    \noindent where $S_{i}$, $L_{i}$, and $E_{i}$ are as defined previously. The logarithmic formulation of this model is

@@

    For each property in link density, generality, and vulnerability, we used the form of the equation that was best supported
    when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
    We then simplified each model following the same procedure as for the relationships between
    latitude and food-web properties, except that species richness was retained in all reduced models.

@@

  Link density, generality, and vulnerability each increased with increasing
  species richness (Fig~\ref{props_v_lat}; $\beta_0$=0.666,
  $p$\textless0.001; $\beta_0$=0.623, $p$\textless0.001; and
  $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine, marine,
  and terrestrial food webs the strength of this scaling did not vary with
  latitude ($\beta_{Latitude}$=-0.001, $p$=0.267 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.363 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.005, $p$=0.008;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.002; and
  $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In stream food
  webs generality increased more rapidly towards the poles
  ($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability
  did not vary with latitude.

  Unlike species richness, only generality showed an overall increase with increasing
  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
  density, generality, and vulnerability respectively,
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estuarine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
  $p$=0.006, respectively; Fig.~\ref{BIT}). For the scaling of link density and
  vulnerability in marine and terrestrial communities, the overall effect of
  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
  there was little overall scaling relationship. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
  exponents for marine and terrestrial communities were not significantly
  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001).

  As with species richness, link density, generality, and vulnerability
  generally increased with the proportion of intermediate consumers in a web
  ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}).
  The strength of this scaling decreased towards the poles in estuarine,
  lake, marine, and stream communities in each case
  ($\beta_{Latitude}$=-0.012, $p$=0.007; $\beta_{Latitude}$=-0.018,
  $p$\textless0.001; and $\beta_{Latitude}$=-0.012, $p$=0.007, respectively;
  Fig~\ref{BIT}). In terrestrial communities, however, scaling was stronger
  towards the  poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for
  link density; $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for
  generality; and $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.022 for
  vulnerability, respectively).

  In contrast, link density, generality, and vulnerability decreased as the
  proportion of top predators increased ($\beta_0$=-0.511, $p$\textless0.001;
  $\beta_0$=-0.418, $p$\textless0.001; and $\beta_0$=-0.511, $p$\textless0.001
  respectively; Fig~\ref{props_v_lat}). For estuarine, lake, and marine
  food webs the strength of this scaling did not
  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.527 for
  link density; $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the
  best-fit model for generality did not include any terms for latitude in
  any ecosystem type). In stream and terrestrial food webs, scaling was more
  strongly negative in the tropics and did not differ from zero near the poles,
  although this trend was only significant in streams
  ($\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link density;
  $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{BIT}).

@@

  Our results were inconsistent with the latitude-niche breadth hypothesis in estuarine, marine,
  and terrestrial communities but consistent with the hypothesis of greater specialisation
  in the tropics in stream and lake food webs. This suggests that different mechanisms may structure
  food webs in different habitat types and that freshwater food webs in particular may be strongly
  affected by seasonal variation. In addition, different relationships between latitude and niche
  breadth in different habitat types goes some way towards explaining the equivocal support for
  the opposing hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader 
  niche space in the tropics~\citep{Davies2007}; both have merit but appear
  to apply to different systems.

@@

\section*{Figures}
\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) 
against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values corrected for
ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). For
the uncorrected values, see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

% \begin{figure}[H]
% \includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
% \caption{Scaling relationships for link density, generality (number of prey), 
% and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
% intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
% For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
% any effects of habitat type or latitude (N=163 food webs). }
% \label{props_v_lat_obs}
% \end{figure}

% \newpage

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empirical food webs. 
Exponents for the scaling of generality and vulnerability with species richness were very 
similar to those for link density, except for the scaling of generality in streams where 
the size of the exponent increased towards the poles. See \emph{Fig. S2, Appendix 5} for 
all scaling relationships.}
\label{S}
\end{figure}

\begin{figure}[!H]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.
Exponents for the scaling relationships of generality and vulnerability with each proportion were very
similar to those of the scaling relationships with link density, except for the scaling of generality
with the proportion of top predators where there was no effect of latitude on the size of the exponent
in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
\label{BIT}
\end{figure}

>>>>

\title{Generality in food webs scales with species richness but not with latitude}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2, Canada\\
\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\}

@@

\vspace{-0.3 in}

@@

Several properties of food webs---the networks of feeding links between
species---are known to vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships with species richness
in the estuarine, marine, and terrestrial food webs, there were strong effects
of latitude on scaling relationships in the freshwater food webs. In these
communities, the latitude-niche breadth hypothesis appears to hold true while
in other habitat types niche breadth appears to vary little. These contrasting
findings indicate that it may be more important to account for habitat than
latitude when exploring gradients in food-web structure.

@@

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialisation (i.e., the breadth of the Eltonian niche ~\citep{Elton1927}) of species within food webs.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics(~\citealp{Dyer2007,Marra1997};
  but see~\citealp{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness. If this is
  the case, it may still be possible to uncover effects of latitude on specialisation by examining the shape of the scaling 
  relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
  latitude affects the scaling of each property with species richness, we test effects of latitude on specialisation implied by
  the ``latitude-niche breadth hypothesis''.

@@

    As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
    is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
    sets to form ``trophic species'' webs ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}. As our study
    is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
    species with identical sets of interactions. We therefore analysed both original and trophic-species versions
    of the dataset; in each case using the number of species and 
    links in each web to calculate the mean link density (number of links per species), mean generality 
    (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
    The version of the dataset used did not qualitatively change the results, suggesting that
    the scaling relationships between species richness, other food-web properties, and latitude are very 
    similar whether or not redundant species are included. For simplicity, here we present only
    the results for the original webs.

@@

    The scaling relationship between link density ($Z$) and species richness ($S$)
    has been shown to be a power law~\citep{Riede2010} of the form

@@

    \noindent As the two forms imply a statistical fit to the data to different error 
    distributions, neither of which has strong
    \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
    to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
    The logarithmic form (equation~\ref{Loglog}) provided the better fit to the data,
    as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
    We therefore used and present logarithmic models throughout the rest of the study.

@@

    After determining the appropriate form of the scaling relationship, we
    then assessed the impact of latitude on the scaling relationships between
    species richness and  link density, generality, vulnerability. In the
    context of the scaling relationships above, note  that this implies that
    we wished to determine the effect of latitude on the scaling exponent
    $\beta$. We included a categorical variable for
    ecosystem type (stream, lake,  terrestrial, marine, or estuary), as well
    as interactions between food web type and latitude.

@@

    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
    marine, lake, and terrestrial networks with estuarine
    networks providing the intercept) and $\epsilon_{i}$ a residual error term.
    The logarithmic formulation of this model is

@@

    We then simplified each model. To do this, we calculated the AIC of the
    maximal model as well as the AIC's of a suite of candidate simplified
    models identified using the R~\citep{R} function dredge from package
    MuMIn~\citep{MuMIn}.  Simplified models were obtained by systematically
    removing all possible combinations  of terms from the full model with the
    restriction that species richness was retained in all reduced models. The
    best-fitting model was then determined to be the model with the fewest
    terms  where $\Delta$AIC\textless2. If several models shared the fewest
    number of terms  and had $\Delta$AIC\textless2, the model with the lowest
    AIC in that set was chosen as the best-fit model.

@@

  Link density, generality, and vulnerability each increased with increasing
  species richness ($\beta_0$=0.643, $p$\textless0.001; $\beta_0$=0.599,
  $p$\textless0.001; and $\beta_0$=0.643, $p$\textless0.001, respectively;
  Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.232 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.257 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.233 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.006;
  $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001; and
  $\beta_{Latitude:Lake}$=0.005, $p$=0.005, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$\textless0.001) while link density and
  vulnerability did not vary with latitude.

  Unlike species richness, only generality showed an overall increase with increasing
  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
  density, generality, and vulnerability, respectively;
  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
  effects of latitude on the scaling relationships. Thus, the scaling
  exponents for link density and vulnerability were negative for estuarine,
  lake, and stream communities and became more negative towards the poles
  ($\beta_{Latitude}$=-0.007, $p$=0.005 and $\beta_{Latitude}$=-0.007,
  $p$=0.005, respectively; Fig.~\ref{BIT}). For the scaling of link density and
  vulnerability in marine and terrestrial communities, the overall effect of
  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
  $p$=0.037; $\beta_{Latitude:Terrestrial}$=0.011, $p$=0.005 and
  $\beta_{Latitude:Marine}$=0.009, $p$=0.036;
  $\beta_{Latitude:Terrestrial}$=0.011, $p$=0.005, respectively) such that
  there was little overall scaling relationship. In contrast, the scaling
  exponent of generality with the proportion of basal resources was positive
  near the equator and negative near the poles in estuarine, lake, and stream
  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
  exponents for marine and terrestrial communities were not significantly
  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.021;
  $\beta_{Latitude:Terrestrial}$=0.014, $p$=0.003).

  As with species richness, link density, generality, and vulnerability
  generally increased with the proportion of intermediate consumers in a web
  ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). The
  strength of this scaling decreased towards the poles in estuarine, lake,
  marine, and stream communities in each case ($\beta_{Latitude}$=-0.012,
  $p$=0.007; $\beta_{Latitude}$=-0.018, $p$\textless0.001; and
  $\beta_{Latitude}$=-0.012, $p$=0.007, respectively; Fig~\ref{BIT}). In
  terrestrial communities, however, scaling was always stronger towards
  the poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for link density;
  $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for generality; and
  $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for vulnerability,
  respectively).

  In contrast, link density, generality, and vulnerability decreased as the
  proportion of top predators increased ($\beta_0$=-0.511, $p$\textless0.001;
  $\beta_0$=-0.418, $p$\textless0.001; and $\beta_0$=-0.511, $p$\textless0.001
  respectively; Fig~\ref{props_v_lat}). For estuarine, lake, and marine
  food webs the strength of this scaling did not
  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.572 for
  link density; $\beta_{Latitude}$=-0.001, $p$=0.566 for vulnerability; the
  best-fit model for generality did not include any terms for latitude in
  any ecosystem type). In stream and terrestrial food webs, scaling was more
  strongly negative in the tropics and did not differ from zero near the poles,
  although this trend was only significant in streams
  ($\beta_{Latitude:Stream}$=0.011, $p$=0.002 and
  $\beta_{Latitude:Terrestrial}$=0.005, $p$=0.136 for link density;
  $\beta_{Latitude:Stream}$=0.012, $p$=0.002 and
  $\beta_{Latitude:Terrestrial}$=0.005, $p$=0.133 for vulnerability; Fig~\ref{BIT}).

@@

  Overall, our results were inconsistent with the latitude-niche breadth
  hypothesis in estuarine, marine, and terrestrial communities but consistent
  with the hypothesis of greater specialisation in the tropics in stream and
  lake food webs. This suggests that different mechanisms may structure food
  webs in different habitat types and that freshwater food webs in particular
  may be strongly affected by seasonal variation. In addition, different
  relationships between latitude and niche breadth in different habitat types
  goes some way towards explaining the equivocal support for the opposing
  hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader
  niche space in the tropics~\citep{Davies2007}; both have merit but appear to
  apply to different systems.

@@

\section*{Figures}
\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to species richness and the proportions of basal resources (\% Basal), intermediate 
consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
and vulnerability were re-scaled to remove the effects of latitude and, where applicable, ecosystem
type by dividing the observed value of link density, generality, or vulnerability by species richness
or the proportion of species at a given trophic level raised to an exponent including the effects of
latitude, ecosystem type, and their interaction. Note that estuarine food webs were used as the intercept
ecosystem type in all models, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
we show these rescaled values (white circles), as well as the overall scaling relationship using estuarine
ecosystems as a baseline (N=163 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=163 empirical food webs.
Latitude is given in degrees from the equator regardless of direction. The
behaviour of exponents for the scaling of generality and vulnerability with
species richness was very  similar to those for link density, except for the
scaling of generality in streams where  the size of the exponent increased
towards the poles. See \emph{Fig. S2, Appendix 5} for  all scaling
relationships.} \label{S} \end{figure}

\begin{figure}[!H]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
on N=163 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
proportion was very similar to those of the scaling relationships with link density, except for the 
scaling of generalitywith the proportion of top predators where there was no effect of latitude on the 
size of the exponent in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
\label{BIT}
\end{figure}
